% =============================================================================
%  MAIN ACADEMIC BASE TEMPLATE — BITCOIN HARMONIC TIME MODEL
% =============================================================================
\documentclass[11pt,a4paper,oneside]{article}

% --- Core Packages ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{siunitx}
\usepackage{float}
\usepackage{hyperref}
\usepackage{microtype}

% --- Page Geometry ---
\geometry{
    a4paper,
    total={160mm,247mm},
    left=25mm,
    top=25mm,
}

% --- SIunitx Configuration ---
\sisetup{
    group-separator={,},
    group-minimum-digits=4
}

% --- Hyperref Setup ---
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={The Bitcoin Harmonic Time Model},
    pdfpagemode=FullScreen,
}

% --- Mathematical Environments ---
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{definition}{Definition}

% =============================================================================
%  METADATA & TITLE CONFIGURATION
% =============================================================================
\title{\textbf{The Bitcoin Harmonic Time Model:\\
Internal Phase Symmetry, Amplitude Power-Laws, and the Institutional ETF Regime Shift}}

\author{\textbf{Romero Quant} \\
\small Independent Quantitative Research \\
\small \texttt{romero.quant@proton.me} \\
\small \href{https://x.com/RomeroQuant}{@RomeroQuant}}

\date{\small June 2026}

% =============================================================================
%  DOCUMENT BODY
% =============================================================================
\begin{document}

\maketitle

\begin{abstract}
This paper formalises the Bitcoin Harmonic Time Model, a two-dimensional quantitative framework that structures Bitcoin market cycles into a discrete dynamic system defined by temporal phase symmetry and compressed amplitude distributions. We demonstrate that the governing clock of the market is not the halving event in isolation, but a stable internal phase architecture where the halving acts as a temporal node, consistently arriving at normalised phase $\bar{\phi}(H) \approx 0.494$ of the expansion phase. Using historical data from three completed cycles, we establish that expansion lasts $1{,}060 \pm 12$ days and contraction $370 \pm 13$ days, yielding a mean period of $1{,}430$ days. Furthermore, we derive an empirical power-law demonstrating that cycle multipliers scale non-linearly with prior drawdown depth ($\hat{\mathcal{M}}(d) = 328 \cdot d^{5.1}$), and introduce a structural adjustment framework to account for the regime shift initiated by the launch of spot US Exchange-Traded Funds (ETFs) in 2024. Finally, we translate this unified model into explicit, dated, and falsifiable calendar hypotheses for the current and subsequent market cycles.
\end{abstract}

\newpage
\tableofcontents
\newpage

% =============================================================================
%  SECTION INTEGRATION (MODULAR INPUTS)
% =============================================================================

% 1. Section 2: Empirical Foundations
\input{section2_empirical_data}

% 2. Sections 3 & 4: Phase Formalisation and Law of Amplitude
\input{sections3_4_amplitude}

% 3. Sections 5, 6 & 7: Synthesis, Projections and Limitations
\input{sections5_6_7_final}

% =============================================================================
%  BIBLIOGRAPHY (Failsafe Empty Setup)
% =============================================================================
\begin{thebibliography}{99}
\bibitem{nakamoto2008}
Nakamoto, S. (2008). \textit{Bitcoin: A Peer-to-Peer Electronic Cash System}. Self-published.
\bibitem{romero2026}
Romero Quant. (2026). \textit{The Invariance of Bitcoin's Internal Expansion Phases}. Quantitative Research Series, Vol. 1.
\end{thebibliography}

\end{document}
% =============================================================================
%  END OF BASE TEMPLATE
% =============================================================================